### 2011-01-21 paper/introduction.tex
Hello all. Good: added HyperNEAT description and lots of comments. Bad, its long, and I don't have HyperNEAT figures in there yet. I'll keep working at it, which will  mean it will likely get longer.
Length will be our enemy. Mark my words <ar har har har har...evil laugh...>
 Good stuff so far Jason!

\editbox{Outline \\
 - Why gait learning is cool \\
 - Gait learning has been done before, in simulation and on hardware (cite, cite, cite) \\
 - HyperNEAT has been used to evolve gaits before in sim (cite, ...) \\
 - Here, we do two cool things for the first time: \\
 - - evolve HN in hardware \\
 - - compare it to other learning methods on the same hardware.}

>>>>

\editbox{Outline \\
 - Why gait learning is cool \\
 - Gait learning has been done before, in simulation and on hardware (cite, cite, cite) \\
 - HyperNEAT has been used to evolve gaits before in simulation~{clune2009evolving, clune2011performance, clune2009hybrid}, and it worked well in part because the gaits were regular, raising the question of whether this high performance was just because the gaits were regular? We test this hypothesis by comparing HyperNEAT to traditional machine learning methods biased towards regular gaits.  \\
 - Here, we do two cool things for the first time: \\
 - - evolve HN in hardware \\
 - - compare it to other learning methods on the same hardware.}

### 2011-01-21 paper/learningMethods.tex
Hello all. Good: added HyperNEAT description and lots of comments. Bad, its long, and I don't have HyperNEAT figures in there yet. I'll keep working at it, which will  mean it will likely get longer.
Length will be our enemy. Mark my words <ar har har har har...evil laugh...>
 Good stuff so far Jason!

\edit{make figure to go here, show drawing with inner/outer, l/r, and f/b motors.}

@@

We implemented and tested 8 different learning strategies.  All
strategies except for the HyperNEAT method\cite{clune} were
constrained to pick parameters from within predetermined ranges.

\begin{itemize}

\item \emph{Random}: This method randomly generates parameter vectors
  in the allowable range. This strategy is used only as baseline.

>>>>

\edit{make figure to go here, show drawing with inner/outer, l/r, and f/b motors.}
\edit{JMC: Use photo of physical robot in this image, and add labels in photoshop?}

@@

We implemented and tested 8 different learning strategies.  All
strategies except for the HyperNEAT method\cite{clune2009evolving} were
constrained to pick parameters from within predetermined ranges.

\edit{JMC:Bullets=narrower column=wasted space. subsubsection instead?}

\begin{itemize}
\item \emph{Random}: This method randomly generates parameter vectors
  in the allowable range. This strategy is used only as baseline.
